

\begin{thebibliography}{99}

\bibitem{author1} Aldinhas Ferreira, Maria Isabel; Fletcher, Sarah R. (2022): The 21st Century Industrial Robot: When Tools Become Collaborators. Cham: Springer International Publishing (81).

 \bibitem{author2} International Organization for Standardization. (2011). Robots and robotic devices - Safety requirements for industrial robots - Part 1: Robots (ISO 10218-1:2011). ISO.

 \bibitem{author3}George Michalos, Panagiotis Karagiannis, Nikos Dimitropoulos, Dionisis Andronas, and Sotiris Makris(2022): Human Robot Collaboration in Industrial Environments: The 21st Century Industrial Robot:  When Tools Become Collaborators.(pp 17-39) Cham: Springer International Publishing (81).\

 \bibitem{author4} Alexandra Dobrokvashina, Shifa Sulaiman, Aidar Zagirov,Elvira Chebotareva, Hsia Kuo-Hsien,Evgeni Magid (uuuu-uuuu): Human Robot Interaction in Collaborative Manufacturing Scenarios: Prospective Cases: IEEE (2022 International Siberian Conference on Control and Communications (SIBCON)).

\bibitem{author5} Murino, Teresa; Di Nardo, Mario; Pollastro, Daniele; Berx, Nicole; Di Francia, Angela; Decré, Wilm et al. (2023): Exploring a cobot risk assessment approach combining FMEA and PRAT. In Quality \& Reliability Eng 39 (3), pp. 706–731. DOI: 10.1002/qre.3252   .

\bibitem{author6} Matheson, Eloise; Minto, Riccardo; Zampieri, Emanuele G. G.; Faccio, Maurizio; Rosati, Giulio (2019): Human–Robot Collaboration in Manufacturing Applications: A Review. In Robotics 8 (4), p. 100. DOI: 10.3390/robotics8040100.

\bibitem{author7} Valori, Marcello; Scibilia, Adriano; Fassi, Irene; Saenz, José; Behrens, Roland; Herbster, Sebastian et al. (2021): Validating Safety in Human–Robot Collaboration: Standards and New Perspectives. In Robotics 10 (2), p. 65. DOI: 10.3390/robotics10020065.

 \bibitem{author8}Weng, Yueh-Hsuan; Chen, Chien-Hsun; Sun, Chuen-Tsai (2009): Toward the Human–Robot Co-Existence Society: On Safety Intelligence for Next Generation Robots. In Int J of Soc Robotics 1 (4), pp. 267–282. DOI: 10.1007/s12369-009-0019-1                          

\bibitem{author9}Hamid Tabani, Francisco J. Cazorla, Guillem Bernat (Ed.) (2019): Assessing the Adherence of an Industrial Autonomous Driving Framework to ISO 26262 Software Guidelines. DAC '19: The 56th Annual Design Automation Conference 2019. Las Vegas NV USA, 02 06 2019 06 06 2019. New York, NY, USA: ACM.

\bibitem{author10}International Organization for Standardization. (2011). Robots and robotic devices - Safety requirements for industrial robots - Part 2: Robots (ISO 10218-2:2011). 

\bibitem{author11} International Organization for Standardization. (2016). Robots and robotic devices — Collaborative robots (ISO/TS 15066).

\bibitem{author12} International Organization for Standardization/International Electrotechnical Commission. (2023). Information technology — Artificial intelligence — Guidance on risk management (ISO/IEC 23894).

\bibitem{author13} Estonian Centre for Standardisation. (2018). EVS-EN IEC 60812:2018 - Analysis techniques for system reliability - Procedure for failure mode and effects analysis (FMEA) (ISO/IEC 60812:2006, IDT). Tallinn, Estonia: EVS.

\bibitem{author14} Li, Jamy; Chignell, Mark (2022): FMEA-AI: AI fairness impact assessment using failure mode and effects analysis. In AI Ethics 2 (4), pp. 837–850. DOI: 10.1007/s43681-022-00145-9.


\bibitem{author15}  Du, Guoguang; Wang, Kai; Lian, Shiguo; Zhao, Kaiyong (2021): Vision-based robotic grasping from object localization, object pose estimation to grasp estimation for parallel grippers: a review. In Artif Intell Rev 54 (3), pp. 1677–1734. DOI: 10.1007/s10462-020-09888-5.

\bibitem{author16} Bonci, Andrea; Cen Cheng, Pangcheng David; Indri, Marina; Nabissi, Giacomo; Sibona, Fiorella (2021): Human-Robot Perception in Industrial Environments: A Survey. In Sensors (Basel, Switzerland) 21 (5). DOI: 10.3390/s21051571.

\bibitem{author17} Brijacak, Inka; Yahyanejad, Saeed; Reiterer, Bernhard; Hofbaur, Michael (2017): Toward Safe Perception in Human-Robot Interaction.

\bibitem{author18} Kaipa, Krishnanand N.; Kankanhalli-Nagendra, Akshaya S.; Kumbla, Nithyananda B.; Shriyam, Shaurya; Thevendria-Karthic, Srudeep Somnaath; Marvel, Jeremy A.; Gupta, Satyandra K. (2016): Addressing perception uncertainty induced failure modes in robotic bin-picking. In Robotics and Computer-Integrated Manufacturing 42, pp. 17–38. DOI: 10.1016/j                .rcim.2016.05.002.

\bibitem{author19} K. Hsiao, M. Ciocarlie, P. Brook (2011): Bayesian grasp planning, in: ICRAWorkshop on Mobile Manipulation: Integrating Perception and Manipulation.

\bibitem{author20} Burgess-Limerick, Ben; Lehnert, Chris; Leitner, Jurgen; Corke, Peter (2022): DGBench: An Open-Source, Reproducible Benchmark for Dynamic Grasping.

\bibitem{author21} Sun, Yu; Falco, Joe; Roa, Maximo A.; Calli, Berk (2022): Research Challenges and Progress in Robotic Grasping and Manipulation Competitions. In IEEE Robot. Autom. Lett. 7 (2), pp. 874–881. DOI: 10.1109/LRA.2021.3129134.

\bibitem{author22} Y. Bekiroglu et al., "Benchmarking Protocol for Grasp Planning Algorithms," in IEEE Robotics and Automation Letters, vol. 5, no. 2, pp. 315-322, April 2020, doi: 10.1109/LRA.2019.2956411.

\bibitem{author23} Bottarel, Fabrizio; Vezzani, Giulia; Pattacini, Ugo; Natale, Lorenzo (2020): GRASPA 1.0: GRASPA is a Robot Arm graSping Performance BenchmArk. In IEEE Robot. Autom. Lett. 5 (2), pp. 836–843. DOI: 10.1109/LRA.2020.2965865.

\bibitem{author24} Sun, Chen; Zhang, Ruihe; Lu, Yukun; Cui, Yaodong; Deng, Zejian; Cao, Dongpu; Khajepour, Amir (2023): Toward Ensuring Safety for Autonomous Driving Perception: Standardization Progress, Research Advances, and Perspectives. In IEEE Trans. Intell. Transport. Syst., pp. 1–19. DOI: 10.1109/TITS.2023.3321309.

\bibitem{author25}P. Skruch, M. Szelest, M. Dlugosz and D. Cieslar, "Safety of Perception Systems in Vehicles of High-Level Motion Automation," 2022 20th International Conference on Emerging eLearning Technologies and Applications (ICETA), Stary Smokovec, Slovakia, 2022, pp. 561-566, doi: 10.1109/ICETA57911.2022.9974838.

\bibitem{author26} Choi, K. L., Kim, M. J., & Kim, Y. M. (2022). On Safety Improvement through Process Establishment for SOTIF Application of Autonomous Driving Logistics Robot. International Journal of Internet, Broadcasting and Communication, 14(1), 209–218. https://doi.org/10.7236/IJIBC.2022.14.1.209

 \bibitem{author27}Mohseni, Sina; Pitale, Mandar; Singh, Vasu; Wang, Zhangyang (2019): Practical Solutions for Machine Learning Safety in Autonomous Vehicles

\bibitem{author28} Madala, Kaushik; Krishnamoorthy, Jayalekshmi; Avalos Gonzalez, Carlos; Shivkumar, Abhishek; Solmaz, Mert (2022): Contributing Factors to Consider While Defining Acceptance Criteria and Validation Targets for Assuring SOTIF in Autonomous Vehicles. In : SAE Technical Paper Series. WCX SAE World Congress Experience, APR. 05, 2022: SAE International400 Commonwealth Drive, Warrendale, PA, United States (SAE Technical Paper Series).

 \bibitem{author29}Peng, Liang; Wang, Hong; Li, Jun (2021): Uncertainty Evaluation of Object Detection Algorithms for Autonomous Vehicles. In Automot. Innov. 4 (3), pp. 241–252. DOI: 10.1007/s42154-021-00154-0.

\bibitem{author30} Hanna, Atieh; Bengtsson, Kristofer; Larsson, Simon; Götvall, Per-Lage (2023): Risk Assessment for Intelligent and Collaborative Automation System by Combining Fmea and Stpa.

\bibitem{author31} Qi, Yi; Dong, Yi; Khastgir, Siddartha; Jennings, Paul; Zhao, Xingyu; Huang, Xiaowei (2023): STPA for Learning-Enabled Systems: A Survey and A New Practice.

\bibitem{author32} STAMATIS, D. H. (2003): Failure mode and effect analysis. FMEA from theory to execution. 2nd ed., rev. and expanded. Milwaukee, Wisconsin: ASQC Quality Press.

\bibitem{author33} Adriaensen, A.; Pintelon, L.; Costantino, F.; Di Gravio, G.; Patriarca, R. (2021): An STPA Safety Analysis Case Study of a Collaborative Robot Application. In IFAC-PapersOnLine 54 (1), pp. 534–539. DOI: 10.1016/j.ifacol.2021.08.061.

 \bibitem{author34} Abdulkhaleq, Asim; Wagner, Stefan; Lammering, Daniel; Boehmert, Hagen; Blueher, Pierre (2017): Using STPA in Compliance with ISO 26262 for Developing a Safe Architecture for Fully Automated Vehicles. DOI: 10.48550/arXiv.1703.03657.

\bibitem{author35} Hanna, Atieh; Larsson, Simon; Götvall, Per-Lage; Bengtsson, Kristofer (2022): Deliberative safety for industrial intelligent human–robot collaboration: Regulatory challenges and solutions for taking the next step towards industry 4.0. In Robotics and Computer-Integrated Manufacturing 78, p. 102386. DOI:10.1016/j.rcim.2022.102386.

\bibitem{author36} Salah, Bashir; Alnahhal, Mohammed; Ali, Mujahid (2023): Risk prioritization using a modified FMEA analysis in industry 4.0. In Journal of Engineering Research. DOI: 10.1016/j.jer.2023.07.001.

\bibitem{author37} Larsson, Simon; Bengtsson, Kristofer (2022): Enabling human-robot collaboration and intelligent automation in the automotive industry: A study of stakeholder perspectives.

\bibitem{author38} Liu, Hu-Chen; Liu, Long; Liu, Nan (2013): Risk evaluation approaches in failure mode and effects analysis: A literature review. In Expert Systems with Applications 40 (2), pp. 828–838. DOI: 10.1016/j.eswa.2012.08.010.

\bibitem{author39} Lee, Sukhan; Lee, Moonju; Kim, Jaewoong; Yoo, Kyeongdae; Barajas, Leandro G; Menassa, Roland (2012): 3D Visual Perception System for Bin Picking in Automotive Sub-Assembly Automation. [Place of publication not identified]: IEEE.

\bibitem{author40} Oh, Jong-Kyu; Lee, Sukhan; Lee, Chan-Ho (2012): Stereo vision based automation for a bin-picking solution. In International Journal of Control, Automation and Systems 10 (2), pp. 362–373. DOI: 10.1007/s12555-012-0216-9.

\bibitem{author41} Sulaman, Sardar Muhammad; Beer, Armin; Felderer, Michael; Höst, Martin (2019): Comparison of the FMEA and STPA safety analysis methods–a case study. In Software Qual J 27 (1), pp. 349–387. DOI: 10.1007/s11219-017-9396-0.

\bibitem{author42} Hanna, Atieh (2021): Towards intelligent and collaborative automation of automotive final assembly. Västerås: Mälardalen University (Mälardalen University Press Licentiate Theses, 305).

\bibitem{author43} Wang, Xuanyu; Qi, Xudong; Wang, Ping; Yang, Jingwen (2021): Decision making framework for autonomous vehicles driving behavior in complex scenarios via hierarchical state machine. In Auton. Intell. Syst. 1 (1). DOI: 10.1007/s43684-021-00015-x.

\bibitem{author44} Pulikottil, Terrin Babu; Pellegrinelli, Stefania; Pedrocchi, Nicola (2021): A software tool for human-robot shared-workspace collaboration with task precedence constraints. In Robotics and Computer-Integrated Manufacturing 67, p. 102051. DOI: 10.1016/j.rcim.2020.102051

\bibitem{author45} Inam, Rafia; Raizer, Klaus; Hata, Alberto; Souza, Ricardo; Forsman, Elena; Cao, Enyu; Wang, Shaolei (2018): Risk Assessment for Human-Robot Collaboration in an automated warehouse scenario. In : 2018 IEEE 23rd International Conference on Emerging Technologies and Factory Automation (ETFA). 2018 IEEE 23rd International Conference on Emerging Technologies and Factory Automation (ETFA). Turin, 04/09/2018 - 07/09/2018: IEEE, pp. 743–751.

\bibitem{author46} Bitsch, Friedemann.; Guiochet, Jérémie.; Skavhaug, Amund. (Eds.) (2016): Computer Safety, Reliability, and Security. 35th International Conference, SAFECOMP 2016, Trondheim, Norway, September 21-23, 2016, Proceedings. Cham: Springer International Publishing; Imprint: Springer (Lecture Notes in Computer Science, 9922).

\bibitem{author46}International Organization for Standardization. (2022). Road Vehicles- Safety of the intended functionality  (ISO 21448:2022). ISO.

\end{thebibliography}

\printbibliography
